The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-07-04 albatros_paper.tex
HCC added more text in section 5

\begin{figure}
  \begin{center}
    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
    \caption{Spectra from a co-aligned polarization pair from the
      two-element \albatros\ pathfinder, shown as a function of
      frequency and time.  The auto- and cross-spectra are shown in
      the top and bottom rows, respectively.  The spectrum magnitudes
      are in uncalibrated ADC units on a logarithmic scale.
      Repeatable structure from the Galaxy is visible over the
      three-day time scale in all plots.}
    \label{Fig:albatros2_waterfalls}
  \end{center}
\end{figure}

@@

The primary goal of the two-element pathfinder described in
\S\ref{s:2elem} was to qualitatively assess the level of RFI and
ionospheric contamination at low frequenices.
\autoref{Fig:albatros2_waterfalls} illustrates auto- and cross-spectra
from one of the co-aligned polarization pairs from the two antennas.
The data are shown over a three-day period (June 18--21, 2018), and no
calibration or cuts have been applied.  The rising and setting of the
Galaxy is visible in all of the spectrum magnitudes, and repeatable
fringes are visible in the phases of the cross-spectra.  The RFI lines
at $\lesssim20$~MHz arise primarily from shortwave radio transmission
reflecting off the ionosphere.  During the night, when the ionospheric
plasma cutoff frequency drops, the maximum frequency of the RFI
contamination falls to $\sim10$~MHz.

As a qualitative illustration of the sky signal repeatability,
\autoref{Fig:albatros2_phase} shows the phases of the cross-spectra
binned in local sidereal time.  About 372 hours of data are averaged
into this plot, and no RFI excision has been performed.  A more
detailed analysis of signal repeatability will be presented in a
future paper, but the high signal-to-noise fringe pattern, which is
even visible a little below $\sim10$~MHz, demonstrates the proof of
concept for building the expanded \albatros\ array.

@@

% \autoref{Fig:waterfall_auto} and \autoref{Fig:waterfall_phase} shows
% the initial results from the two interferometric array.
% \autoref{Fig:waterfall_auto} shows the raw ALBATROS-EGG autospectra
% which where the waterfall plot was taken from one polarization (pol0)
% over an interval of 3 days. The Galaxy rising/setting is clearly
% visible in the structure. There are also ripples in frequency because
% of uncalibrated data, and the ripples arise from reflections in the
% cables. There is a qualitative difference between daytime and
% nighttime data and this shows that the contamination from shortwave
% radio drops off significantly at night, when the ionosphere becomes
% quieter.
% 
% \autoref{Fig:waterfall_phase} shows the first fringes that were
% detected by the the ALBATROS-EGG. The fringes show recurrent structure
% down to a frequency of as low as 10 MHz without data processing or
% data cuts.

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=0.9\linewidth]{Figures/albatros2_waterfalls.jpg}
    \caption{Spectra from a co-aligned polarization pair from the
      two-element \albatros\ pathfinder, shown as a function of
      frequency and time.  The auto- and cross-spectra are shown in
      the top and bottom rows, respectively.  The spectrum magnitudes
      are in uncalibrated ADC units on a logarithmic scale, and the
      cross-spectrum is about two orders of magnitude fainter than the
      autospectra.  Repeatable structure from the Galaxy is visible
      over the three-day time scale in all plots.}
    \label{Fig:albatros2_waterfalls}
  \end{center}
\end{figure}

@@

The primary goal of the two-element pathfinder described in
\S\ref{s:2elem} was to qualitatively assess the level of RFI and
ionospheric contamination at low frequenices.
\autoref{Fig:albatros2_waterfalls} illustrates auto- and cross-spectra
from one of the co-aligned polarization pairs from the two antennas.
The data are shown over a three-day period (June 18--21, 2018), and no
calibration or cuts have been applied.  The rising and setting of the
Galaxy is visible in all of the spectrum magnitudes, and repeatable
fringes are visible in the phases of the cross-spectra.  The signal
drop-off below $\lesssim30$~MHz in the autospectra is caused largely
by the combined response of the LWA antenna and FEE.  Although the LWA
antenna is not optimized for the lowest \albatros\ observing
frequencies, as described in \S\ref{s:antenna}, it is sufficient for
these initial, exploratory measurements.  The RFI lines at
$\lesssim20$~MHz arise primarily from shortwave radio transmission
reflecting off the ionosphere.  During the night, when the ionospheric
plasma cutoff frequency drops, the maximum frequency of the RFI
contamination falls to $\sim10$~MHz.

As a qualitative illustration of the sky signal repeatability,
\autoref{Fig:albatros2_phase} shows the phases of the cross-spectra
binned in local sidereal time.  About 372 hours of data are averaged
into this plot, and no RFI excision has been performed.  A more
detailed analysis of signal repeatability will be presented in a
future paper, but the high signal-to-noise fringe pattern, which is
even visible slightly below $\sim10$~MHz, demonstrates the proof of
concept for building the expanded \albatros\ array.

@@
